GP As If You Meant It: Real and Imaginary User Experience

### 2015-03-29 tex/Book/gpbook-Tozier-2015-03-23/tozier.tex
fixed LaTeX setup per instructions
session.md appendix using definition list (becomes description list in LaTeX)
first draft:

\abstract{(to be written last)}

@@

@@

\bibliographystyle{spbasic}
\bibliography{gp-bibliography,chapter}

>>>>

\abstract{In this contribution I describe a \emph{kata}, or exercise intended for advanced GP users, called ``GP as if you meant it''. In the exercise, the human participant(s) are charged with trying to ``rescue'' an ineffectual but unstoppable GP system which is set up initially to only use ``random guessing''. The exercise is in the form of a game of alternating turns, in which the human ``User'' player is provided complete information but only a very limited toolkit, and the (automated) GP System ``player'' can only be modified and ``adjusted'' by adding new search operators and objectives. The crux of the exercise is the human players' development of cogent \emph{warrants} for every design decision they make when building and using GP systems---decisions which otherwise can be habitual or arbitrary. By explicitly prohibiting the most common response of  ``stop it and restart with different parameters'', the participants are mindful of ways to \emph{accommodate} the noted ``pathologies'' and ``symptoms''. The computational participant tends to just get warmer.}

@@

[version of \today\ at \currenttime]

@@

\bibliographystyle{spbasic}
\bibliography{gp-bibliography,tozier}
